Growing up with Nell: A Narrative Interface for Literacy

### 2012-03-11 paper.tex
Remove 'during development' part of rule groups text.

Other rule groups may invoke random selection, select between stories
based on child preferences, curriculum, or inferred learning style,
or (during development) flag an error to highlight an
unexpected ambiguity.

>>>>

Other rule groups may invoke random selection or select between stories
based on child preferences, curriculum, or inferred learning style.
